---
title: "SESYNC Cyber Training Summer Institute"
author: "Janardan & Holly"
date: "7/26/2019"
output: html_document
---

## Social-Ecological Narratives Graduate Pursuit  

#### Leveraging Social-Ecological Narratives for Sustainability Insights: How Do Environmental Conditions and Perceptions Interact Along Maine’s Storied Coast?  


**Collaborators**

* Janardan Mainali
* Holly Cronin
* Melissa Kimble
* Andrew Sellers
* Kacey Stewart
* Anna Woodhead  

**Introduction**

This Graduate Pursuit aims to explore the role of narratives within social-ecological system dynamics. We define these **social-ecological narratives** as *the stories through which communities understand their interactions and co-dependencies with an ecological system*. Our methods rely on data integration and analysis across natural sciences, social sciences, and humanities--in particular [natural language processing](https://cran.r-project.org/web/views/NaturalLanguageProcessing.html) of under-utilized data from literary, media, and other textual sources.


Our project proposes to apply this approach to the case-study of oysters (*Crassostrea virginica*) in coastal Maine. Here we present our initial approach to prepare a variety of text-based data sources for analysis.


### Overview of Preparations for Text Analysis  


![Figure 6.1: A flowchart of a text analysis that incorporates topic modeling. The topicmodels package takes a Document-Term Matrix as input and produces a model that can be tided by tidytext, such that it can be manipulated and visualized with dplyr and ggplot2. Source: https://www.tidytextmining.com/topicmodeling.html](https://www.tidytextmining.com/images/tidyflow-ch-6.png)

* Convert various documents to standardized .txt files using template header (thanks Melissa!)

```
        START HEADER
        SOURCE: 
        TITLE: 
        AUTHOR: 
        DATE:
        LOCATION:
        TYPE:  
        END HEADER

        This is the body, or primary text of the article.
```
  
* Collect .txt files into a corpus of documents and create a [corpus object](https://www.tidytextmining.com/dtm.html#tidying-corpus-objects-with-metadata) in RStudio   

```{r}
setwd("/nfs/senarratives-data")
## RegEx
#We read corpus from the literary source and code our way to document matrix(?)

library(stringr)
library(tm)

ourCorpus <- VCorpus(DirSource("/nfs/senarratives-data/NewsLiterarySources"))


```

* Extract data (header and body text) from each document in corpus to create a single table with header items and body as columns

```{r}

setwd('/nfs/senarratives-data/NewsLiterarySources')
file.names<-list.files(path = '/nfs/senarratives-data/NewsLiterarySources', pattern = ".txt")


#Creating coloumn names
mySource1= character(0)
myTitle1= character(0)
myAuthor1= character(0)
myDate1= character(0)

library(stringr)
for(i in file.names){
  print(i)
  #Here I am trying to read the text files by line so that I can extract the info
  myFile <- read.delim(i,
                       "\n",
                       quote = "",
                       row.names = NULL,
                       stringsAsFactors = FALSE,
                       header= FALSE)
  mySource<- str_remove(myFile$V1[2], "SOURCE:") #str_remove uses stringr package. I needed it to remove unwanted text from the cell of our interest.
  myTitle<- str_remove(myFile$V1[3],"TITLE: ")
  myAuthor<-str_remove(myFile$V1[4], "AUTHOR: ")
  myDate<-str_remove(myFile$V1[5], "DATE:")

  #Let me append these to separate coloumns
  mySource1= append(mySource1, mySource)
  myTitle1= append(myTitle1, myTitle)
  myAuthor1= append(  myAuthor1, myAuthor)
  myDate1= append( myDate1, myDate)
}

myMeta<- cbind(mySource1, myTitle1, myAuthor1, myDate1)
#myMeta

#write.csv( myMeta, file= "C:/SESYNC_Workshop/Resources_TXT/sen_table.csv")


```

* Clean data...

```{r}

## Cleaning texts from our corpus

library(magrittr)

sen_words <- ourCorpus %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>% #Removes stop words like and, the, a etc.
  tm_map(stripWhitespace)

remove_link<- function(body) {
  match <- str_detect(body, '(http|www|mailto)')
  body[!match]
}

sen_words <- sen_words %>%
  tm_map(content_transformer(remove_link))

## Stopwords and Stems

sen_words <- sen_words %>%
  tm_map(stemDocument) %>%
  tm_map(removeWords, stopwords("english"))

```

* Create a [document term matrix](https://cran.r-project.org/web/packages/tidytext/vignettes/tidying_casting.html)  

```{r}

## Bag-of-Words

dtm <- DocumentTermMatrix(sen_words)

## Long Form

library(tidytext)
library(dplyr)
dtt <- tidy(dtm) #recognizes pattern and 
words <- dtt %>%
  group_by(term) %>%
  summarise(
    n = n(),
    total = sum(count)) %>%
  mutate(nchar = nchar(term))

dtt_trimmed <- words %>%
  filter(
    nchar < 16,
    n > 1,
    total > 3) %>%
  select(term) %>%
  inner_join(dtt)

dtm_trimmed <- dtt_trimmed %>%
  cast_dtm(document, term, count) #tidytext package

## Term Correlations

word_assoc <- findAssocs(dtm_trimmed, 'oyster' , 0.6) #from tm package. We are checking correlations with oyster*
word_assoc <- data.frame(
  word = names(word_assoc[[1]]),
  assoc = word_assoc,
  row.names = NULL)




```

* Use a Latent Dirichlet allocation (LDA) to fit a topic model

```{r}

## Latent Dirichlet allocation

library(topicmodels)

seed = 12345 #for random generator. Just to make sure same process happens every time it is run
fit = LDA(dtm_trimmed, k = 5, control = list(seed=seed))
email_topics <- as.data.frame(
  posterior(fit, dtm_trimmed)$topics)




```

* Create a set of word clouds to present results of topic modeling
```{r}

library(ggwordcloud)

topics <- tidy(fit) %>%
  filter(beta > 0.006) #How tightly associated with the topic

ggplot(topics,
       aes(size = beta, label = term)) +
  geom_text_wordcloud_area(rm_outside = TRUE) +
  facet_wrap(vars(topic))


```
* Some sentiment analysis

```{r}
## Let us run some sentiment analysis
library(dplyr)
library(tidytext)

sen_td<- tidy(dtm_trimmed)

sen_sentiments <- sen_td %>%
  inner_join(get_sentiments("bing"), by = c(term = "word"))

sen_sentiments

library(ggplot2)

sen_sentiments %>%
  count(sentiment, term, wt = count) %>%
  ungroup() %>%
  filter(n >= 18) %>%
  mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
  mutate(term = reorder(term, n)) %>%
  ggplot(aes(term, n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  ylab("Contribution to sentiment") +
  coord_flip()
```

* Let's take a look and try to interpret our preliminary results...

![Results of preliminary topic modeling for corpus of documents related to oysters in Maine (n.b. sample data used is just a ~20 document subset of our text data) ](Insert github link to png file here)  

* Now that we have a sense of what people are discussing, how are they feeling about these topics? Let's see if we can gain any insights by using sentiment analysis

```
{r}

[Insert sentiment analysis code here :)]

```

![Results of preliminary sentiment analysis for corpus of documents related to oysters in Maine (n.b. sample data used is just a ~20 document subset of our text data) ](Insert github link to png file here) 

```{r pressure, echo=FALSE}
plot(pressure)
```

* Next steps: to explore word frequency over time and think about options for geolocating the documents within our corpus to link with other data types and map narrative...
